---
title: "SNA_prac6"
author: "Yidi Yan"
date: "04/03/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Appendix 
```{r, include = FALSE}
library(statnet)
load("data_lab6.RData")

###############################################################
### Question (a)
class(elist.lazega.df) #edge list
class(v.attr.lazega) #node attributes

#transform edge list to matrix
mat.lazega.df <- data.matrix(elist.lazega.df)
class(mat.lazega.df)

lazega.net <- network(mat.lazega.df, matrix.type = "edgelist", directed = FALSE, names.eval = "strength")
class(lazega.net)
summary(lazega.net, print.adj = FALSE)
plot(lazega.net)

as.sociomatrix(lazega.net,"strength") #binary adjacency matrix 
plot(lazega.net, displaylabels = T)

#adding attributes 
set.vertex.attribute(lazega.net, "name", c(1:36))
lazega.net %v% "sex" <- v.attr.lazega$Gender
lazega.net %v% "senior" <- v.attr.lazega$Seniority
lazega.net %v% "status" <- v.attr.lazega$Status
lazega.net %v% "office" <- v.attr.lazega$Office
lazega.net %v% "years" <- v.attr.lazega$Years
lazega.net %v% "age" <- v.attr.lazega$Age
lazega.net %v% "practice" <- v.attr.lazega$Practice
lazega.net %v% "school" <- v.attr.lazega$School
lazega.net %v% "indegree" <- degree(lazega.net, cmode = "indegree")

list.vertex.attributes(lazega.net)
get.vertex.attribute(lazega.net, "vertex.names")

library(igraph)
inet <- graph.edgelist(mat.lazega.df)
class(inet)
V(inet)$name <- paste("V",c(1:36))
E(inet)$val <- c(1:115)
summary(inet)

library(intergraph)
ilazega.net <- asIgraph(lazega.net)
class(ilazega.net)

library(netCoin)
V(ilazega.net)$name <- V(ilazega.net)$vertex.names

visualize.broswer <- function(graph){
  nodes <- as.data.frame(vertex_attr(graph, "name"))
  colnames(nodes) <- "name"
  nodes$name <- as.character(nodes$name)
  nodes$indegree <- degree(graph, mode = "in")
  nodes$outdegree <- degree(graph, mode = "out")
  net <- allNet(incidence=as_adjacency_matrix(graph),nodes=nodes)
  plot(net)
}
  
visualize.broswer(ilazega.net)


###############################################################
### Question (b)
detach(package:igraph)
library(statnet)
library(ggplot2)
par(mar = rep(0.15, 4))
plot(lazega.net, displaylabels = T, vertex.cex=3, label.cex=0.5, label.pos=5, pad=0.1)
png(filename = "lazega.png", width = 10000, height = 5000, pointsize = 100)
plot(lazega.net, displaylabels = T, vertex.cex=3, label.cex=0.5, label.pos=5, pad=0.1)
dev.off()

# diagram 1 
nodeColours <- ifelse(v.attr.lazega$Gender=="1", "dodgerblue", "hotpink")
lazega.school.factor <- as.factor(v.attr.lazega$School)
cex_age <- v.attr.lazega$Age
side_nb <- 3:7

par(mar = rep(0.2,4))
gplot(lazega.net, mode = "kamadakawai", 
      label = v.attr.lazega$Office, label.cex=0.6, pad=0.1, #label
      arrowhead = F, vertex.col = nodeColours, #color
      vertex.sides = side_nb[lazega.school.factor], #node shape
      vertex.cex = log(cex_age-30)-1.2) #node size 
legend("bottom", legend = c("Male", "Female"), col = c("dodgerblue","hotpink"), pch=19, pt.cex=1.5, title = "Gender")
legend("bottomleft", legend = c("Office 1", "Office 2", "Office 3"), title = "Node label")
title("Kamada-Kawai layout algorithm", line = -2)

# diagram 2
lazega.practice.factor <- as.factor(v.attr.lazega$Practice)
cex_yrs <- v.attr.lazega$Years
side_nb <- 3:7

par(mar = rep(0.2,4))
gplot(lazega.net, mode = "kamadakawai", 
      label = v.attr.lazega$School, label.cex=0.6, pad=0.1, #label
      arrowhead = F, vertex.col = nodeColours, #color
      vertex.sides = side_nb[lazega.practice.factor], #node shape
      vertex.cex = log(cex_yrs)-1) #node size 
legend("bottom", legend = c("Male", "Female"), col = c("dodgerblue","hotpink"), pch=19, pt.cex=1.5)
legend("bottomleft", legend = c("School 1", "School 2", "School 3"), title = "Node label")
legend("bottomright", legend = c("Practice 1", "Practice 2"), pch = c(0,2))
title("Kamada-Kawai layout algorithm", line = -2)


###############################################################
## Question (c)
gden(lazega.net)
is.connected(lazega.net)
is.connected(lazega.net, connected = "weak")


###############################################################
## Question (d)

#node centrality 
deg <- degree(lazega.net,rescale = TRUE)
summary(deg)

#closeness centrality
lazega.gdist <- geodist(lazega.net)$gdist
which(lazega.gdist[,1]=="Inf")
sum(1/lazega.gdist[1,2:network.size(lazega.net)])
closeness2 <- function(x){
  geo <- 1/geodist(x)$gdist
  diag(geo) <- 0
  apply(geo,1,sum)
}
close2 <- closeness2(lazega.net)

#betweenness centrality 
between <- betweenness(lazega.net)

#centralization
centralization(lazega.net, degree, cmode = "indegree")

cd <- centralization(lazega.net, degree)
cc <- centralization(lazega.net, closeness, cmode = "suminvdir")
cb <- centralization(lazega.net, betweenness)
#Bonacich power centrality 
detach(package:statnet)
library(igraph)
power_centrality(ilazega.net)


##############################################################
## Question (e)
library(igraph)
library(intergraph) 
#k-core structure analysis
lazega.coreness <- graph.coreness(ilazega.net)
table(lazega.coreness)

kc<-kcores(lazega.net, cmode="indegree")
#plot the nest of cores
gplot(lazega.net, displaylabels = TRUE, usearrows = FALSE,vertex.col=rainbow(max(kc)+1)[kc+1])
#plot only 2-core 
gplot(lazega.net[kc>1,kc>1], displaylabels = TRUE, vertex.col=rainbow(max(kc)+1)[kc[kc>1]+1])

V(ilazega.net)$name <- get.vertex.attribute(ilazega.net, name = "vertex.names", index = V(ilazega.net))
V(ilazega.net)$color <- lazega.coreness + 1

lay <- layout.fruchterman.reingold(ilazega.net)
op <- par(mfrow=c(1,2), mar = rep(0,4))
# In igraph, name attribute is used by default to label the nodes in a plot
plot(ilazega.net, vertex.size = 15, vertex.label.cex = 0.7, edge.arrow.size = 0.5, layout=lay) 
# Label the nodes with their k-core membership value
plot(ilazega.net, vertex.label = lazega.coreness, vertex.label.cex = 0.7, edge.arrow.size = 0.5, layout=lay) 
par(op)

ilazega.net_core1 <- induced.subgraph(ilazega.net, vids = which(lazega.coreness >= 1))
ilazega.net_core3 <- induced.subgraph(ilazega.net, vids = which(lazega.coreness >= 3))
ilazega.net_core5 <- induced.subgraph(ilazega.net, vids = which(lazega.coreness >= 5))

lay <- layout.fruchterman.reingold(ilazega.net)
op <- par(mfrow=c(2,2), mar = c(2,0,2,0))
plot(ilazega.net, vertex.label = lazega.coreness, layout = lay, main = "All k-cores", edge.arrow.size = 0.1)
plot(ilazega.net_core1, vertex.label = lazega.coreness[which(lazega.coreness >=1)], layout = lay[which(lazega.coreness >=1),], main = "k-cores 1+", edge.arrow.size = 0.1)
plot(ilazega.net_core3, vertex.label = lazega.coreness[which(lazega.coreness >=3)], layout = lay[which(lazega.coreness >=3),], main = "k-cores 3+", edge.arrow.size = 0.1)
plot(ilazega.net_core5, vertex.label = lazega.coreness[which(lazega.coreness >=5)], layout = lay[which(lazega.coreness >=5),], main = "k-cores 5+", edge.arrow.size = 0.1)


###############################################################
## Question (f)

mod_sex <- modularity(ilazega.net, V(ilazega.net)$sex, weights = E(ilazega.net)$strength) 
mod_office <- modularity(ilazega.net, V(ilazega.net)$office, weights = E(ilazega.net)$strength) 
mod_years <- modularity(ilazega.net, V(ilazega.net)$years, weights = E(ilazega.net)$strength) 
mod_age <- modularity(ilazega.net, V(ilazega.net)$age, weights = E(ilazega.net)$strength) 
mod_practice <- modularity(ilazega.net, V(ilazega.net)$practice, weights = E(ilazega.net)$strength) 
mod_school <- modularity(ilazega.net, V(ilazega.net)$school, weights = E(ilazega.net)$strength) 

mod_table <- matrix(c(mod_sex, mod_office, mod_years, mod_age, mod_practice,mod_school), 
                    ncol = 6, byrow = T)
colnames(mod_table) <- c("Sex", "Office", "Years", "Age", "Practice", "School")
rownames(mod_table) <- "Modularity"
as.table(mod_table)


###############################################################
## Question (g)

# remove the isolates 
detach(package:igraph)
library(statnet)
lazega.iso.net <- lazega.net
delete.vertices(lazega.iso.net, isolates(lazega.iso.net))
lazega.iso <- lazega.iso.net
plot(lazega.iso)
ilazega.iso <- asIgraph(lazega.iso)

detach(package:statnet)
library(igraph)
lazega.cw <- cluster_walktrap(ilazega.iso)
class(lazega.cw)
membership(lazega.cw)
mod_cw <- modularity(lazega.cw)

#using network with isolates 
lazega.edge <- cluster_edge_betweenness(ilazega.net)
mod_edge <- modularity(lazega.edge)

lazega.greedy <- cluster_fast_greedy(ilazega.net)
mod_greedy <- modularity(lazega.greedy)

#plots
par(mfrow=c(2,2), mar = c(2,0,2,0))
lay2 <- layout.fruchterman.reingold(ilazega.iso)
lay3 <- layout.fruchterman.reingold(ilazega.net)
plot(lazega.cw, ilazega.iso, vertex.label = V(ilazega.iso)$office, layout = lay2, main = "Walktrap")
plot(lazega.edge, ilazega.net, vertex.label = V(ilazega.net)$office, layout = lay3, main = "Edge betweenness")
plot(lazega.greedy, ilazega.net, vertex.label = V(ilazega.net)$office, layout = lay3, main = "Fastgreedy")

mod_table_argo <- matrix(c(mod_cw, mod_edge, mod_greedy), ncol = 3, byrow = T)
colnames(mod_table_argo) <- c("Walktrap", "Edge Betweenness", "Fastgreedy")
rownames(mod_table_argo) <- "Modularity"
as.table(mod_table_argo)

```


```{r, eval=FALSE, echo=FALSE}
suppressPackageStartupMessages(source("practice6_assess.R"))
```

## Question (a)
```{r, eval=TRUE, echo=FALSE}
summary(lazega.net, print.adj = FALSE)
```
In the Lazega network, the data is undirected and binary. The network data has eight node attributes and all attributes are integer valued. The attributes `name` and `seniority` is identical for each person ranging from 1 to 36; `sex` and `practice` are coded as 1 and 2; `office` and `school` are classified as 1,2,3; `years` is integer ranging from 1 to 32; and `status` is 1 for all nodes. 
From the summary function, there are 115 edges and the overall density is 0.1825397. 

## Question (b)
```{r, eval=TRUE, echo=FALSE} 
#diagram 1
par(mar = rep(0.3,4)) 
gplot(lazega.net, mode = "kamadakawai", 
      label = v.attr.lazega$Office, label.cex=0.6, pad=0.1, #label
      arrowhead = F, vertex.col = nodeColours, #color
      vertex.sides = side_nb[lazega.school.factor], #node shape
      vertex.cex = log(cex_age-30)-1.2) #node size 
legend("bottom", legend = c("Male", "Female"), col = c("dodgerblue","hotpink"), pch=19, pt.cex=1.5, title = "Gender")
legend("bottomleft", legend = c("Office 1", "Office 2", "Office 3"), title = "Node label")
title("Kamada-Kawai layout algorithm - diagram 1", line = -2)

#diagram 2
par(mar = rep(0.2,4))
gplot(lazega.net, mode = "kamadakawai", 
      label = v.attr.lazega$School, label.cex=0.6, pad=0.1, #label
      arrowhead = F, vertex.col = nodeColours, #color
      vertex.sides = side_nb[lazega.practice.factor], #node shape
      vertex.cex = log(cex_yrs)-1) #node size 
legend("bottom", legend = c("Male", "Female"), col = c("dodgerblue","hotpink"), pch=19, pt.cex=1.5)
legend("bottomleft", legend = c("School 1", "School 2", "School 3"), title = "Node label")
legend("bottomright", legend = c("Practice 1", "Practice 2"), pch = c(0,2))
title("Kamada-Kawai layout algorithm - diagram 2", line = -2) 

```


## Question (c)

The density of the network is 0.1825, indicates that the network is not well-connected. From the first graph, lawyers in the network are not well-connected and two lawyers who are not connected with any other lawyers in the network. Three female lawyers are structured closely even though not all three female lawyers are connected to each other. There is not a clear pattern that the network has any structure in relation to the law school they went to. The node label indicates that lawyers are more connected within the same office. The node size indicates that lawyers with different age groups are well mixed.   

From the second graph, still, three female lawyers are structured to be close to each other. The square shape nodes are centred in the network shows that lawyers working in the same practice are better connected. The size of the nodes indicates the years the lawyer has been working within the firm, and the graph shows that some nodes with smaller size are clusted into two groups. 

In conclusion, collaboration is relatively structured by the lawyers' attributes, especially their gender, office, years working within the firm and types of practice.


## Question (d)
```{r, eval=TRUE, echo=FALSE}
detach(package:igraph)
library(statnet)
#node centrality
summary(deg)
#network centralization
centralization(lazega.net, degree, cmode = "indegree")
#closeness centrality
close2
hist(close2, breaks = 10)
#betweenness centrality
between
hist(between, breaks = 10)
#Bonacich Power Centrality
detach(package:statnet)
library(igraph)
power_centrality(ilazega.net)
summary(power_centrality(ilazega.net))
sum(power_centrality(ilazega.net) > 0)
```

**Node centrality** represents the direct connections one node has divided by the maximum possible connections. The maximum degree centrality in this network is 0.06522 and the mean degree centrality is only 0.02778, which is very low.  

The **network centralization** is 0.2530612, is much higher than the node centrality. 

**Closeness centrality** represents the distance of one node to other nodes.The histogram shows that except for two nodes which are isolated, other nodes have similar closeness.  

**Betweenness centrality** represents the geopath between the node and other nodes. The histogram shows that the majority of nodes have small betweenness while some nodes have very large betweenness.  

The **Bonacich Power Centrality** and its summary are shown above. Positive Bonacich power centrality indicates that the node's connections have many connections, and it's increasing the node's power. Negative Bonacich power centrality indicates that the node's connections have few connections, and it's decreasing the node's power. The Bonacich power centrality in this network ranges from -2.24 to 0.55, and on average, people in this network have negative Bonacich power centrality. Only 4 people out of 36 have positive Bonacich power centrality and they are considered as powerful people in this group. 


## Question (e)
```{r, eval=TRUE, echo=FALSE}
op <- par(mfrow=c(2,2), mar = c(2,0,2,0))
plot(ilazega.net, vertex.label = lazega.coreness, layout = lay, main = "All k-cores", edge.arrow.size = 0.1)
plot(ilazega.net_core1, vertex.label = lazega.coreness[which(lazega.coreness >=1)], layout = lay[which(lazega.coreness >=1),], main = "k-cores 1+", edge.arrow.size = 0.1)
plot(ilazega.net_core3, vertex.label = lazega.coreness[which(lazega.coreness >=3)], layout = lay[which(lazega.coreness >=3),], main = "k-cores 3+", edge.arrow.size = 0.1)
plot(ilazega.net_core5, vertex.label = lazega.coreness[which(lazega.coreness >=5)], layout = lay[which(lazega.coreness >=5),], main = "k-cores 5+", edge.arrow.size = 0.1)
```

K-core analysis is a decomposition of the whole group into subgroups, uncovering the network's hierarchical and structural properties. 

## Question (f)
```{r, eval=TRUE, echo=FALSE}
as.table(mod_table)
```

The modularity statistic represents the extent to which a node grouping variable explains the observed clustering. The modularity statistic can range from -1/2 to +1. The closer to 1, the more the network clustering follows the given node grouping. The table above shows the modularities using six node attributes. From the table, the modularity using Office is closest to 1, thus which office does the lawyer work is the best predictor of the network clustering. 

## Question (g)
```{r, eval=TRUE, echo=FALSE}
#modularity table
as.table(mod_table_argo)

#plot
plot(lazega.cw, ilazega.iso, vertex.label = V(ilazega.iso)$office, layout = lay2, main = "Walktrap")
```

The walktrap community detection algorithms uses network data without two isolates, the edge betweenness and fast-greedy algorithms use the orginal netowrk data. From the modularity table, using walktrap algorithms shows the highest modularity, thus it's the best solution. 





